Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-07-02 ms.tex
fixed the error in the plot shows LW phot after moving the centroid using the SW
added a few plots and note on persistence from AZ lab 01

@@

\subsection{Asic Dewar Tests}

We also explored the difference between resets per frame versus resets per integrations as discussed in Section \ref{sec:preAmp}.
We used a stripe mode 2048x256 with reference pixels on the bottom and sides.
\begin{figure*}
{\gridline{\fig{rpf_vs_rpi_old_cds_no_refpix.pdf}{0.99\textwidth}{No Reference Pixels RPF}}}
{\gridline{\fig{rpf_vs_rpi_new_cds_with_refpix.pdf}{0.99\textwidth}{Reference Pixel RPF}}}
\caption{Reset per frame with reference pixel correction.}\label{fig:RPFrefpix}
\end{figure*}

>>>>

\begin{figure*}
%\gridline{\fig{tser_LW_OTIS.pdf}{0.99\textwidth}{WLP8 Image} }
\gridline{\fig{tser_LWSW_OTIS_w_shift.pdf}{0.6\textwidth}{Grism Time Series}}
\caption{Same as Figure \ref{fig:otisLWSWtser} but where the SW shifts were applied (with a scaling factor of 0.5) to the long wave.
The aperture shifting appears to increase the flux errors with centroid shifts.
}\label{fig:otisLWSWtserShift}
\end{figure*}

@@

\clearpage
\subsection{Asic Dewar Tests}

\subsubsection{Persistence}
HST shows noticeable ramps with each HST orbit due to detector charge trapping \citep{zhou2017chargeTrap}.
Lamp sources in our laboratory tests typically have a warm up period lasting several tens of minutes, which makes it difficult to observe this same effect the detector ramps.
However, the charge trap release time is expected to the same when illuminated as compared to when turning the lamp off.
We therefore show a time series of an LED after it is turned off in Figure \ref{fig:persistence}.
In this experiment, the detectors are illuminated for 3 hours with fluence levels of about 300 DN/s for 53 seconds.
Thus, they are safely under saturation.
The charge trapping release becomes undetectable after 10 minutes and is well below 0.1 DN/s.

\begin{figure*}
{\gridline{\fig{ap_labels_B4persistence_AZLabStab01refcor.pdf}{0.5\textwidth}{Box Apertures}}}
{\gridline{\fig{phot_B4persistence_AZLabStab01refcor_tser.pdf}{0.5\textwidth}{Persistence Time Series}}}
\caption{Persistence decays rapidly, indicating .}\label{fig:persistence}
\end{figure*}

\subsubsection{Pre-Ampflier Reset Test}
We also explored the difference between resets per frame versus resets per integrations as discussed in Section \ref{sec:preAmp}.
We used a stripe mode 2048x256 with reference pixels on the bottom and sides.
\begin{figure*}
{\gridline{\fig{rpf_vs_rpi_old_cds_no_refpix.pdf}{0.99\textwidth}{No Reference Pixels RPF}}}
{\gridline{\fig{rpf_vs_rpi_new_cds_with_refpix.pdf}{0.99\textwidth}{Reference Pixel RPF}}}
\caption{Reset per frame with reference pixel correction.}\label{fig:RPFrefpix}
\end{figure*}
